Application with Lakes Data

### 2021-10-13 inst/scripts/application.Rmd
section 3 and 4 edits

```{r, results = "hide"}
set.seed(320215)
data_sf <- sf::st_as_sf(USlakes, coords = c("XCOORD", "YCOORD"),
                        crs = 5070)
library(spsurvey)
grts_samp <- grts(data_sf, n_base = n)
grts_bind <- sprbind(grts_samp)

>>>>

```{r, results = "hide"}
set.seed(320215)
data_sf <- sf::st_as_sf(USlakes, coords = c("XCOORD", "YCOORD"),
                        crs = 5070)
library(spsurvey)
grts_samp <- grts(data_sf, n_base = n)
grts_bind <- sp_rbind(grts_samp)
